---
title: "CodeBook"
author: "JeffLi"
date: "November 18, 2014"
output: html_document
---

## Data Description
The experiments have been carried out with a group of 30 volunteers within an age bracket of 19-48 years. Each person performed six activities (`WALKING`, `WALKING_UPSTAIRS`, `WALKING_DOWNSTAIRS`, `SITTING`, `STANDING`, `LAYING`) wearing a smartphone (Samsung Galaxy S II) on the waist. Using its embedded accelerometer and gyroscope, we captured 3-axial linear acceleration and 3-axial angular velocity at a constant rate of 50Hz. The experiments have been video-recorded to label the data manually. The obtained dataset has been randomly partitioned into two sets, where 70% of the volunteers was selected for generating the training data and 30% the test data. 

1.First row of the Code, indicates that this project need package "dplyr", if you don't have one, install it.
```{r}
require(dplyr)
```

2.Then, use method `read.table` to read data from txt files, and store them in variables.
```{r}
features <- read.table("UCI HAR Dataset/features.txt")
activity_label <- read.table("UCI HAR Dataset/activity_labels.txt")
train_set <- read.table("UCI HAR Dataset/train/X_train.txt")
train_subject <- read.table("UCI HAR Dataset/train/subject_train.txt")
train_label <- read.table("UCI HAR Dataset/train/y_train.txt")
test_set <- read.table("UCI HAR Dataset/test/X_test.txt")
test_subject <- read.table("UCI HAR Dataset/test/subject_test.txt")
test_label <- read.table("UCI HAR Dataset/test/y_test.txt")
```

3.Give those variables in these data sets with appropriately labels
```{r}
names(train_set) <- features$V2
names(train_subject)<-"Subject"
names(train_label) <- "Activity"
names(test_set) <- features$V2
names(test_subject)<-"Subject"
names(test_label) <- "Activity"
```

4. Extracts only the measurements on the mean and standard deviation for each measurement. And use `rbind` command to merge them.
```{r}
train_set_part <- train_set[,grepl("mean|std",names(train_set))]
test_set_part <- test_set[,grepl("mean|std",names(test_set))]
train_data <- cbind(train_subject,train_label,train_set_part)
test_data <- cbind(test_subject,test_label,test_set_part)
data <- rbind(train_data,test_data)
```

5. Give those activity with descriptive activity names. And write those tidydata into tidydata.txt in your workspace
```{r}
data$Activity <- activity_label[data$Activity,][,2]
write.table(data, "tidydata.txt")
```

6.Finally, Let's see what's the processed data look like
```{r}
head(data[,1:5])
```





